Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-18 cordillera-cycle.tex
Typeset: fix figure paths in typset.
To allow for diffs.
Typeset: some table formatting.
I purposely did not apply all changes from the typesetter.

\begin{table*}
  \centering
  \caption{Parameter values used in the ice sheet model.}
  \label{tab:params}
  {\begin{tabular}{llrl}
    \tophline
    Not.    & Name & Value & Unit \\
    \middlehline

    $\rho$  & Ice density
            & 910
            & \unit{kg\,m^{-3}} \\

    $g$     & Standard gravity
            & 9.81
            & \unit{m\,s^{-2}} \\

    \multicolumn{2}{l}{\emph{Basal sliding}} \\

    $q$     & Pseudo-plastic sliding exponent
            & 0.25
            & - \\

@@

    $\delta$& Effective pressure coefficient
            & 0.02
            & - \\

    $e_0$   & Till reference void ratio
            & 0.69
            & - \\

    $C_{\mathrm{c}}$   & Till compressibility coefficient
            & 0.12
            & - \\

    $W_{\text{max}}$ & Maximal till water thickness
            & 2.0
            & m \\

    \multicolumn{2}{l}{\emph{Bedrock and lithosphere}} \\

    $\rho_{\mathrm{b}}$& Bedrock density
            & 3300
            & \unit{kg\,m^{-3}} \\

@@

    $D$     & Lithosphere flexural rigidity
            & $5.0\times10^{24}$
            & \unit{N} \\

    \multicolumn{2}{l}{\emph{Surface and atmosphere}} \\

    $T_{\mathrm{s}}$   & Temperature of snow precipitation
            & 273.15
            & \unit{K} \\

@@

    $\gamma$& Air temperature lapse rate
            & $6\times10^{-3}$
            & \unit{K\,m^{-1}} \\

    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22\,\unit{ka} after scaling.}
  \label{tab:records}
  {\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (\unit{m\,a.s.l.}) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & -5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

@@

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & -3038
             & \chem{U^{K'}_{37}}
             & 1.20 & -6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

\begin{table*}
  \caption{Extremes in Cordilleran ice sheet volume and extent corresponding to
           MIS~4, 3 and 2 for each of the six low-resolution simulations
           (Fig.~\ref{fig:lr_ts}).}
  \label{tab:extrema}
  {\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m\,s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     &  57.45 &  42.93 &  19.14
             &   1.87 &   0.69 &   2.07
             &   7.35 &   1.69 &   8.71 \\
    NGRIP    &  60.25 &  45.86 &  22.85
             &   2.11 &   0.74 &   2.10
             &   8.84 &   1.82 &   8.76 \\
    EPICA    &  61.89 &  45.30 &  17.23
             &   1.51 &   1.01 &   2.09
             &   5.11 &   2.74 &   8.91 \\
    Vostok   &  60.86 &  41.25 &  16.84
             &   1.51 &   1.03 &   2.01
             &   5.15 &   2.88 &   8.40 \\
    ODP 1012 &  56.46 &  47.39 &  23.19
             &   1.38 &   0.90 &   2.07
             &   4.39 &   2.35 &   8.62 \\
    ODP 1020 &  60.23 &  52.97 &  20.56
             &   1.25 &   0.72 &   2.09
             &   3.84 &   1.75 &   8.81 \\
    \middlehline
    Minimum  &  61.89 &  52.97 &  23.19
             &   1.25 &   0.69 &   2.01
             &   3.84 &   1.69 &   8.40 \\
    Maximum  &  56.46 &  41.25 &  16.84
             &   2.11 &   1.03 &   2.10
             &   8.84 &   2.88 &   8.91 \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

>>>>

\begin{table*}
\caption{Parameter values used in the ice sheet model.}
\label{tab:params}
%\scalebox{.85}[.85]
{\begin{tabular}{llrl}
    \tophline
    Not.    & Name & Value & Unit \\
    \middlehline
    $\rho$  & Ice density
            & 910
            & \unit{kg\,m^{-3}} \\

    $g$     & Standard gravity
            & 9.81
            & \unit{m\,s^{-2}} \\
    \cline{1-4}
    \multicolumn{2}{l}{{Basal sliding}} \\
    \cline{1-4}
    $q$     & Pseudo-plastic sliding exponent
            & 0.25
            & -- \\

@@

    $\delta$& Effective pressure coefficient
            & 0.02
            & -- \\

    $e_0$   & Till reference void ratio
            & 0.69
            & -- \\

    $C_{\mathrm{c}}$   & Till compressibility coefficient
            & 0.12
            & -- \\

    $W_{\text{max}}$ & Maximal till water thickness
            & 2.0
            & m \\
    \cline{1-4}
    \multicolumn{2}{l}{{Bedrock and lithosphere}} \\
    \cline{1-4}
    $\rho_{\mathrm{b}}$& Bedrock density
            & 3300
            & \unit{kg\,m^{-3}} \\

@@

    $D$     & Lithosphere flexural rigidity
            & $5.0\times10^{24}$
            & \unit{N} \\
    \cline{1-4}
    \multicolumn{2}{l}{{Surface and atmosphere}} \\
    \cline{1-4}
    $T_{\mathrm{s}}$   & Temperature of snow precipitation
            & 273.15
            & \unit{K} \\

@@

    $\gamma$& Air temperature lapse rate
            & $6\times10^{-3}$
            & \unit{K\,m^{-1}} \\
    \bottomhline
\end{tabular}}
\end{table*}

\begin{table*}
  \caption{%
Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22\,\unit{ka} after scaling.}
\label{tab:records}
%\scalebox{.850}[.850]
{\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (\unit{m\,a.s.l.}) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & -5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

@@

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & -3038
             & \chem{U^{K'}_{37}}
             & 1.20 & -6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}

\begin{table*}
\caption{%
Extremes in Cordilleran ice sheet volume and extent corresponding to
           MIS~4, 3 and 2 for each of the six low-resolution simulations
           (Fig.~\ref{fig:lr_ts}).}
\label{tab:extrema}
%\scalebox{.50}[.50]
{\begin{tabular}{l|ccc|ccc|ccc}
    \tophline
             & \multicolumn{3}{c|}{Age (ka)}
             & \multicolumn{3}{c|}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m\,s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     &  57.45 &  42.93 &  19.14
             &   1.87 &   0.69 &   2.07
             &   7.35 &   1.69 &   8.71 \\
    NGRIP    &  60.25 &  45.86 &  22.85
             &   2.11 &   0.74 &   2.10
             &   8.84 &   1.82 &   8.76 \\
    EPICA    &  61.89 &  45.30 &  17.23
             &   1.51 &   1.01 &   2.09
             &   5.11 &   2.74 &   8.91 \\
    Vostok   &  60.86 &  41.25 &  16.84
             &   1.51 &   1.03 &   2.01
             &   5.15 &   2.88 &   8.40 \\
    ODP 1012 &  56.46 &  47.39 &  23.19
             &   1.38 &   0.90 &   2.07
             &   4.39 &   2.35 &   8.62 \\
    ODP 1020 &  60.23 &  52.97 &  20.56
             &   1.25 &   0.72 &   2.09
             &   3.84 &   1.75 &   8.81 \\
    \cline{1-10}
    Minimum  &  61.89 &  52.97 &  23.19
             &   1.25 &   0.69 &   2.01
             &   3.84 &   1.69 &   8.40 \\
    Maximum  &  56.46 &  41.25 &  16.84
             &   2.11 &   1.03 &   2.10
             &   8.84 &   2.88 &   8.91 \\
    \bottomhline
\end{tabular}}
\end{table*}
